atlantisom: simulated ecosystem datasets for assessment model performance testing

### 2020-06-09 atlantisom_landingpage.Rmd
streamline

![A wide range of models exist to address potential fishery management questions](docs/images/ecomods.png)

### How do we know our models are right?

 * Fits to historical data (hindcast)

 * Influence of data over time (retrospective diagnostics)

 * Keep as simple and focused as possible

 * Simulation testing

But what if data are noisy? What if we need to model complex interactions? What if conditions change over time?

@@

### Illustration: Climate impacts in the operating model 
![Changing sardine habitat](docs/images/sardinetempIsaac.png)

Hodgson, E. E., Kaplan, I. C., Marshall, K. N., Leonard, J., Essington, T. E., Busch, D. S., Fulton, E. A., et al. 2018. Consequences of spatially variable ocean acidification in the California Current: Lower pH drives strongest declines in benthic species in southern regions while greatest economic impacts occur in northern regions. Ecological Modelling, 383: 106–117.

Marshall, K. N., Kaplan, I. C., Hodgson, E. E., Hermann, A., Busch, D. S., McElhany, P., Essington, T. E., et al. 2017. Risks of ocean acidification in the California Current food web and fisheries: ecosystem model projections. Global Change Biology, 23: 1525–1539.

### Illustration: Climate + cumulative impacts in the operating model 
![Habitat changes lead to changes in both populations and community interactions over time](docs/images/guildbioIsaac.png)

## How does this affect the "data" for stock assessments?

The atlantisom user must specify uncertainty in assessment "data":

@@

@@

## What can atlantisom do so far?

@@

## A "sardine" assessment

>>>>

Assessing the ability of models to predict key processes is essential if the models are to be used in decision-making dependent on those processes. Skill assessment compares model predictions with observations; good agreement between predictions and observations indicates high skill (see, e.g. [Stow et al 2009](https://www.sciencedirect.com/science/article/abs/pii/S0924796308001103)). However, in many natural resrouce management contexts, the observations themselves are highly uncertain, so assessing model skill can be difficult. In these cases, creating an observational dataset with a simulation model can provide alternative information for model skill assessment.

@@

## How does `atlantisom` make "data" for stock assessments?

The `atlantisom` user must specify uncertainty in assessment "data":

@@

Using these specifications, `atlantisom` generates survey data from the true biomass outputs of the Atlantis model, and generates fishery data from the true fishery outputs of the Atlantis model. The simulated data can then be used as inputs to a variety of single species or multispecies assessment models.

@@

## Visualizing `atlantisom` outputs

@@

## Example: a "sardine" assessment
